A Handbook for Tenured Track Faculty in Computer Science in the US

### 2024-09-12 faculty.tex
updates

\chapter{Teaching}\label{chapter}

@@

\section{Teaching Load}
New TT faculty often have a lighter teaching load in their first several years or even throughout their tenure track.  This is to give you time to establish your research program.  However, you should expect to teach at least one course per semester. The teaching load is usually higher at teaching universities, and lower at research universities.

The desirable teaching load for TT at most R1 universities is 1+1 (1 course / semester) during the tenure track. While some univs might give you a lighter load in your first year, most univs expect you to teach 1+1 from your second year. In many cases, 1+1 is only for the first 2 or 3 years and after that it increases to 1+2 (or 2+1). It is rare that a TT in CS at R1 universities would have to teach 2+2 during the tenure track.

In many cases, your contract might list 1+1 for the first X year and 1+2 after until tenure, but the dept unofficial gives TT faculty 1+1 until tenure. This is because the dept chair can reduce the teaching load based on performance. There are also other ways to reduce teaching load such as \emph{buying out} of teaching with a grant, leading a very large grant, or have taught many large classes.

TT faculty will teach both undergrad and grad courses.  Grad courses include seminars, special topics, and core courses.  Most new faculty use seminars and special topics to recruit students for their research group.  Undergrad courses are typically higher level courses in your area of expertise (e.g., 400 level course on Software Testing).  It is rare that you have to teach 100 level courses (e.g., Intro to Programming) because there are just too many students in these courses.

@@

  At UNL, TT faculty is 1+1 for the first 3 years, and 1+2 after that.  At GMU, it is 1+1 for the first 3 years, but I haven't seen any TT faculty having to teach more than that during their tenure track. In addition, GMU grants all TT faculty a semester off from teaching before tenure. Some faculty use this to work on their NSF CAREER proposal while others use it to prepare their tenure application.

@@

@@

\section{Teaching Philosophy}
\section{Teaching Awards}

\chapter{Mentoring}

>>>>

\chapter{Teaching}\label{chapter:teaching}

@@

\section{Teaching Load}
New TT faculty often have a lighter teaching load in their first several years or even throughout their tenure track.  This is to give you time to establish your research program. The teaching load is usually higher at teaching universities, and lower at research universities.

The desirable teaching load for TT at most R1 universities is 1+1 (1 course / semester). While some univs might give you a lighter load in your first year, most univs expect you to teach 1+1 from your second year. In many cases, 1+1 is only for the first 2 or 3 years and after that it increases to 1+2 (or 2+1). It is rare that a TT in CS at R1 universities would have to teach 2+2 during the tenure track.

In many cases, your contract might list 1+1 for the first X year and 1+2 after until tenure, but the dept unofficial gives TT faculty 1+1 until tenure. Some other ways to reduce teaching load such as \emph{buying out} of teaching with a grant, leading a very large grant, or have taught many large classes.

@@

    At UNL, TT faculty is 1+1 for the first 3 years, and 1+2 after that.  At GMU, it is 1+1 for the first 3 years, but I haven't seen any TT having to teach more than that. In addition, GMU grants all TT faculty a semester off from teaching before tenure. Some faculty use this to work on their NSF CAREER proposal while others use it to prepare their tenure application.

@@

\section{Courses}TT faculty will teach both undergrad and grad courses.  Grad courses include seminars, special topics, and core courses.  Most new faculty use seminars and special topics to recruit students for their research group.  Undergrad courses are typically higher level courses in your area of expertise (e.g., 400 level course on Software Testing). It is rare that you have to teach 100 level courses (e.g., Intro to Programming) because there are just too many students in these courses.

Most depts. would allow faculty to pick their favorite courses to teach.  In some cases, they might ask you to teach an existing core undergraduate courses (e.g., Theory, Operating Systems) and develop your own grad course (e.g., Software Verification).
It is likely that you will repeat the same courses. This significant reduces the amount of time you need to prepare for the course.  However, you should not teach the same course every semester, and you will want to alternate between grad and undergrad courses.

    At GMU, I teach the same Software Specification and Construction course at both grad (SWE-619) and undergrad (SWE-419) levels.  While it is a bit boring to teach the same materials every semester, it is also nice because I don't have to prepare much for the course.  I did try to teach an AI Assurance seminar course once, but never liked it much because it only has MS students, who were not very interested in research.

    In contrast, I teach various courses at UNL. I teach the several undergraduate courses including Theory and design my own two courses on Compilers and Software Analysis. I also create a grad seminar on Software Verification. 
  \end{commentbox}

@@

\section{Recruiting Students for Research} Many TT faculty use their teaching to recruit students for their research group.  Seminar and special topics courses are designed to introduce grad students to your research area. Similarly, you might be able to recruit undergrads from your 400 level courses.  Taking students from your class has the benefits that you and the students already know each other, and you know their strengths and weaknesses, e.g., through their programming assignments in your class.

\chapter{Recruiting and Mentoring}
